---
title: "multi-omics feature set generator"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(imputeTS)
library(EFS)
library(tidyr)
library(plyr)
```

read in data (pasted)
```{r}
all_data = read.csv("all_data_and_min_meta.csv")
```

subset data
```{r}
train_data = subset(all_data, Split_Group == "train")
testing_data = subset(all_data, Split_Group == "test")
```


Make metadata categories for training
```{r}
SES_score = train_data$SES_CD_Score
SES_group = train_data$SES_group
Ulcer_group = train_data$Ulcer_group
Hist_loc = train_data$Historic_location
active_loc = train_data$Active_Location
activity_level = train_data$Activity_level
diagnosis = train_data$Diagnosis
IBDGroup = train_data$Study_group
samples = train_data$OTU_ID
```


Make metadata categories for testing subset
```{r}
IBD_testing_samples = testing_data$OTU_ID

CDvUC_testing_samples = subset(testing_data, Diagnosis == "CD" | Diagnosis == "UC")
CDvUC_testing_samples = CDvUC_testing_samples$OTU_ID

UC_testing_samples = subset(testing_data, Diagnosis == "UC")
CDCol_testing_samples = subset(testing_data, Active_Location == "colonic")
CDColvUC_testing_samples = rbind(UC_testing_samples, CDCol_testing_samples)
CDColvUC_testing_samples = CDColvUC_testing_samples$OTU_ID

CDil_testing_samples = subset(testing_data, Active_Location == "ileal")
CDilvUC_testing_samples = rbind(UC_testing_samples, CDil_testing_samples)
CDilvUC_testing_samples = CDilvUC_testing_samples$OTU_ID


CDUlcer_testing_samples = subset(testing_data, Ulcer_group == "rem_mild" | Ulcer_group == "mod_sev")
CDUlcer_testing_samples = CDUlcer_testing_samples$OTU_ID

CD_CVIC_testing_samples = subset(testing_data, Active_Location == "colonic" | Active_Location == "ileocolonic")
CD_CVIC_testing_samples = CD_CVIC_testing_samples$OTU_ID

CD_IVC_testing_samples = subset(testing_data, Active_Location == "ileal" | Active_Location == "colonic")
CD_IVC_testing_samples = CD_IVC_testing_samples$OTU_ID

CD_IVIC_testing_samples = subset(testing_data, Active_Location == "ileal" | Active_Location == "ileocolonic")
CD_IVIC_testing_samples = CD_IVIC_testing_samples$OTU_ID

CD_NVIC_testing_samples = subset(testing_data, Active_Location == "none" | Active_Location == "ileocolonic")
CD_NVIC_testing_samples = CD_NVIC_testing_samples$OTU_ID

CD_NVI_testing_samples = subset(testing_data, Active_Location == "none" | Active_Location == "ileal")
CD_NVI_testing_samples = CD_NVI_testing_samples$OTU_ID

CD_NVC_testing_samples = subset(testing_data, Active_Location == "none" | Active_Location == "colonic")
CD_NVC_testing_samples = CD_NVC_testing_samples$OTU_ID

SES_MIvMS_testing_samples = subset(testing_data, SES_group == "inactive_mild" | SES_group == "moderate_severe")
SES_MIvMS_testing_samples = SES_MIvMS_testing_samples$OTU_ID

```

Make map of samples in each training subset
```{r}
##main data subsets
TRAIN_CD_data = subset(train_data, Diagnosis == "CD")
TRAIN_IBD_data = subset(train_data, Study_group == "IBD")

## CD v UC
TRAIN_CDvUC_samples = TRAIN_IBD_data$OTU_ID


## train location sample vectors
TRAIN_NVI_data = subset(TRAIN_CD_data, Active_Location == "none" | Active_Location == "ileal")
TRAIN_NVI_samples = TRAIN_NVI_data$OTU_ID

TRAIN_NVIC_data = subset(TRAIN_CD_data, Active_Location == "none" | Active_Location == "ileocolonic")
TRAIN_NVIC_samples = TRAIN_NVIC_data$OTU_ID

TRAIN_NVC_data = subset(TRAIN_CD_data, Active_Location == "none" | Active_Location == "colonic")
TRAIN_NVC_samples = TRAIN_NVC_data$OTU_ID

TRAIN_IVC_data = subset(TRAIN_CD_data, Active_Location == "ileal" | Active_Location == "colonic")
TRAIN_IVC_samples = TRAIN_IVC_data$OTU_ID

TRAIN_IVIC_data = subset(TRAIN_CD_data, Active_Location == "ileal" | Active_Location == "ileocolonic")
TRAIN_IVIC_samples = TRAIN_IVIC_data$OTU_ID

TRAIN_CVIC_data = subset(TRAIN_CD_data, Active_Location == "colonic" | Active_Location == "ileocolonic")
TRAIN_CVIC_samples = TRAIN_CVIC_data$OTU_ID


## train SES subsets
TRAIN_SES_MIvMS_data = subset(TRAIN_CD_data, SES_group == "inactive_mild" | SES_group == "moderate_severe")
TRAIN_SES_MIvMS_samples = TRAIN_SES_MIvMS_data$OTU_ID

## train ulcer group
TRAIN_ULCER = TRAIN_CD_data
TRAIN_ULCER_samples = TRAIN_ULCER$OTU_ID

## CD colonic vs UC
CD_colonic = subset(TRAIN_CD_data, Active_Location == "colonic")
UC = subset(TRAIN_IBD_data, Diagnosis == "UC")
CDCol_v_UC = rbind(CD_colonic,UC)
CDCol_v_UC_samples = CDCol_v_UC$OTU_ID

## CD ileal vs UC
CD_ileal = subset(TRAIN_CD_data, Active_Location == "ileal")
CDil_v_UC = rbind(CD_ileal,UC)
CDil_v_UC_samples = CDil_v_UC$OTU_ID
```

make data frame
```{r}
df = train_data[,9:length(train_data)]
df2 = testing_data[,9:length(testing_data)]
```

Healthy vs IBD comparison
```{r}
## main data set
IBDCompare = cbind(Group = IBDGroup, df)
## recode data
IBDCompare$Group <- as.numeric(revalue(IBDCompare$Group, c("IBD"=1, "HC"=0)))

```

CD vs UC subset, recoding diagnosis
```{r}
#make DFs
CDvUC = cbind(diagnosis, df)

## subset IBD only samples
CDvUC = subset(CDvUC, diagnosis == "CD" | diagnosis == "UC")

## recode data
CDvUC$diagnosis = as.numeric(revalue(CDvUC$diagnosis, c("CD" = 1, "UC" = 0)))

```

CD current location subset
```{r}
## make df
CDOnly = cbind(diagnosis, active_loc, df)

## subset out CD only
CDOnly = subset(CDOnly, diagnosis == "CD")

## subset of locations, binary comparisons
CD_NVI = subset(CDOnly, CDOnly$active_loc == "none" | CDOnly$active_loc == "ileal")
CD_NVC = subset(CDOnly, CDOnly$active_loc == "none" | CDOnly$active_loc == "colonic")
CD_NVIC = subset(CDOnly, CDOnly$active_loc == "none" | CDOnly$active_loc == "ileocolonic")
CD_IVC = subset(CDOnly, CDOnly$active_loc == "ileal" | CDOnly$active_loc == "colonic")
CD_IVIC = subset(CDOnly, CDOnly$active_loc == "ileal" | CDOnly$active_loc == "ileocolonic")
CD_CVIC = subset(CDOnly, CDOnly$active_loc == "colonic" | CDOnly$active_loc == "ileocolonic")

## remove diagnosis column
CD_NVI$diagnosis = NULL
CD_NVC$diagnosis = NULL
CD_NVIC$diagnosis = NULL
CD_IVC$diagnosis = NULL
CD_IVIC$diagnosis = NULL
CD_CVIC$diagnosis = NULL

## recode location
CD_NVI$active_loc = as.numeric(revalue(CD_NVI$active_loc, c("none" = 0, "ileal" = 1)))
CD_NVC$active_loc = as.numeric(revalue(CD_NVC$active_loc, c("none" = 0, "colonic" = 1)))
CD_NVIC$active_loc = as.numeric(revalue(CD_NVIC$active_loc, c("none" = 0, "ileocolonic" = 1)))
CD_IVC$active_loc = as.numeric(revalue(CD_IVC$active_loc, c("ileal" = 0, "colonic" = 1)))
CD_IVIC$active_loc = as.numeric(revalue(CD_IVIC$active_loc, c("ileal" = 0, "ileocolonic" = 1)))
CD_CVIC$active_loc = as.numeric(revalue(CD_CVIC$active_loc, c("colonic" = 0, "ileocolonic" = 1)))

```

Ulcer subsets
```{r}
## make df
CDOnlyUlcer = cbind(diagnosis, Ulcer_group, df)
CDOnlyUlcer = subset(CDOnlyUlcer, CDOnlyUlcer$diagnosis == "CD")
CDOnlyUlcer = subset(CDOnlyUlcer, CDOnlyUlcer$Ulcer_group == "rem_mild" | CDOnlyUlcer$Ulcer_group == "mod_sev")
CDOnlyUlcer$diagnosis = NULL

CDOnlyUlcer$Ulcer_group = as.numeric(revalue(CDOnlyUlcer$Ulcer_group, c("rem_mild" = 0, "mod_sev" = 1)))

```

SES Group subsets
```{r}
SES_data = cbind(diagnosis, SES_group, df)
SES_MIvMS = subset(SES_data, SES_data$SES_group == "inactive_mild" | SES_data$SES_group == "moderate_severe")
SES_MIvMS$diagnosis = NULL
SES_MIvMS$SES_group = as.numeric(revalue(SES_MIvMS$SES_group, c("inactive_mild" = 0, "moderate_severe" = 1)))
```


```{r}
CDColvUC = cbind(diagnosis, active_loc, df)
CDColvUC = subset(CDColvUC, diagnosis == "UC" | active_loc == "colonic")
Colon = ifelse(CDColvUC$diagnosis == "UC", 0,1)
CDColvUC = cbind(Colon, CDColvUC)

CDColvUC$diagnosis = NULL
CDColvUC$active_loc = NULL

CDilvUC = cbind(diagnosis, active_loc, df)
CDilvUC = subset(CDilvUC, diagnosis == "UC" | active_loc == "ileal")
ileal = ifelse(CDilvUC$diagnosis == "UC", 0,1)
CDilvUC = cbind(ileal, CDilvUC)

CDilvUC$diagnosis = NULL
CDilvUC$active_loc = NULL
```



cant get EFS loop to work and don't have time, brute force!
```{r}
##IBD
IBDvHC_EFS = ensemble_fs(IBDCompare, 1, runs = 10)

##CDvUC
CDvUC_EFS = ensemble_fs(CDvUC, 1, runs = 10)

##CD_location
CD_NVI_EFS = ensemble_fs(CD_NVI, 1, runs = 10)
CD_NVC_EFS = ensemble_fs(CD_NVC, 1, runs = 10)
CD_NVIC_EFS = ensemble_fs(CD_NVIC, 1, runs = 10)
CD_IVC_EFS = ensemble_fs(CD_IVC, 1, runs = 10)
CD_IVIC_EFS = ensemble_fs(CD_IVIC, 1, runs = 10)
CD_CVIC_EFS = ensemble_fs(CD_CVIC, 1, runs = 10)

##CD_SES_severity
SES_MIvMS_EFS = ensemble_fs(SES_MIvMS, 1, runs = 10)

##colonic_CD_V_UC
CDColvUC_EFS = ensemble_fs(CDColvUC, 1, runs = 10)

## ileal CD vs UC
CDilvUC_EFS = ensemble_fs(CDilvUC, 1, runs = 10)

## CD ulcer
CDOnlyUlcer_EFS = ensemble_fs(CDOnlyUlcer, 1, runs = 10)
```

```{r}
##gene_names = cbind(Gene_name = protein_annotation$Protein.names, protein = protein_annotation$queryID)
##gene_names = as.data.frame(gene_names)
```


```{r}
EFS_level = 0.4
```


```{r}
IBDvHC_EFS_score_sum = colSums(IBDvHC_EFS) # add sum of scores
IBDvHC_EFS_protsums = rbind(IBDvHC_EFS, IBDvHC_EFS_score_sum) # attach summed score for filtering in future step
## rownames(IBDvHC_EFS_protsums)[rownames(IBDvHC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
IBDvHC_EFS_protsumsT = t(IBDvHC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
IBDvHC_EFS_protsumsT = as.data.frame(IBDvHC_EFS_protsumsT) # made data frame
IBDvHC_EFS_prot25 = subset(IBDvHC_EFS_protsumsT, IBDvHC_EFS_protsumsT$IBDvHC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
IBDvHC_EFS_prot25$SUM = NULL #remove SUM column
IBDvHC_EFS_prot25$protein = rownames(IBDvHC_EFS_prot25) #add protein column if not showing up
IBDvHC_EFS_pro25tLong = gather(IBDvHC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## IBDvHC_EFS_pro25tLong = merge(gene_names, IBDvHC_EFS_pro25tLong) #merge gene_names
ggplot(IBDvHC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```


```{r}
CDvUC_EFS_score_sum = colSums(CDvUC_EFS) # add sum of scores
CDvUC_EFS_protsums = rbind(CDvUC_EFS, CDvUC_EFS_score_sum) # attach summed score for filtering in future step
## rownames(CDvUC_EFS_protsums)[rownames(CDvUC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CDvUC_EFS_protsumsT = t(CDvUC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CDvUC_EFS_protsumsT = as.data.frame(CDvUC_EFS_protsumsT) # made data frame
CDvUC_EFS_prot25 = subset(CDvUC_EFS_protsumsT, CDvUC_EFS_protsumsT$CDvUC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CDvUC_EFS_prot25$SUM = NULL #remove SUM column
CDvUC_EFS_prot25$protein = rownames(CDvUC_EFS_prot25) #add protein column if not showing up
CDvUC_EFS_pro25tLong = gather(CDvUC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CDvUC_EFS_pro25tLong = merge(gene_names, CDvUC_EFS_pro25tLong) #merge gene_names
ggplot(CDvUC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CD_CVIC_EFS_score_sum = colSums(CD_CVIC_EFS) # add sum of scores
CD_CVIC_EFS_protsums = rbind(CD_CVIC_EFS, CD_CVIC_EFS_score_sum) # attach summed score for filtering in future step
rownames(CD_CVIC_EFS_protsums)[rownames(CD_CVIC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CD_CVIC_EFS_protsumsT = t(CD_CVIC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CD_CVIC_EFS_protsumsT = as.data.frame(CD_CVIC_EFS_protsumsT) # made data frame
CD_CVIC_EFS_prot25 = subset(CD_CVIC_EFS_protsumsT, CD_CVIC_EFS_protsumsT$CD_CVIC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CD_CVIC_EFS_prot25$SUM = NULL #remove SUM column
CD_CVIC_EFS_prot25$protein = rownames(CD_CVIC_EFS_prot25) #add protein column if not showing up
CD_CVIC_EFS_pro25tLong = gather(CD_CVIC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_CVIC_EFS_pro25tLong = merge(gene_names, CD_CVIC_EFS_pro25tLong) #merge gene_names
ggplot(CD_CVIC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CD_IVC_EFS_score_sum = colSums(CD_IVC_EFS) # add sum of scores
CD_IVC_EFS_protsums = rbind(CD_IVC_EFS, CD_IVC_EFS_score_sum) # attach summed score for filtering in future step
rownames(CD_IVC_EFS_protsums)[rownames(CD_IVC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CD_IVC_EFS_protsumsT = t(CD_IVC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CD_IVC_EFS_protsumsT = as.data.frame(CD_IVC_EFS_protsumsT) # made data frame
CD_IVC_EFS_prot25 = subset(CD_IVC_EFS_protsumsT, CD_IVC_EFS_protsumsT$CD_IVC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CD_IVC_EFS_prot25$SUM = NULL #remove SUM column
CD_IVC_EFS_prot25$protein = rownames(CD_IVC_EFS_prot25) #add protein column if not showing up
CD_IVC_EFS_pro25tLong = gather(CD_IVC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_IVC_EFS_pro25tLong = merge(gene_names, CD_IVC_EFS_pro25tLong) #merge gene_names
ggplot(CD_IVC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CD_IVIC_EFS_score_sum = colSums(CD_IVIC_EFS) # add sum of scores
CD_IVIC_EFS_protsums = rbind(CD_IVIC_EFS, CD_IVIC_EFS_score_sum) # attach summed score for filtering in future step
rownames(CD_IVIC_EFS_protsums)[rownames(CD_IVIC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CD_IVIC_EFS_protsumsT = t(CD_IVIC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CD_IVIC_EFS_protsumsT = as.data.frame(CD_IVIC_EFS_protsumsT) # made data frame
CD_IVIC_EFS_prot25 = subset(CD_IVIC_EFS_protsumsT, CD_IVIC_EFS_protsumsT$CD_IVIC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CD_IVIC_EFS_prot25$SUM = NULL #remove SUM column
CD_IVIC_EFS_prot25$protein = rownames(CD_IVIC_EFS_prot25) #add protein column if not showing up
CD_IVIC_EFS_pro25tLong = gather(CD_IVIC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_IVIC_EFS_pro25tLong = merge(gene_names, CD_IVIC_EFS_pro25tLong) #merge gene_names
ggplot(CD_IVIC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CD_NVC_EFS_score_sum = colSums(CD_NVC_EFS) # add sum of scores
CD_NVC_EFS_protsums = rbind(CD_NVC_EFS, CD_NVC_EFS_score_sum) # attach summed score for filtering in future step
rownames(CD_NVC_EFS_protsums)[rownames(CD_NVC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CD_NVC_EFS_protsumsT = t(CD_NVC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CD_NVC_EFS_protsumsT = as.data.frame(CD_NVC_EFS_protsumsT) # made data frame
CD_NVC_EFS_prot25 = subset(CD_NVC_EFS_protsumsT, CD_NVC_EFS_protsumsT$CD_NVC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CD_NVC_EFS_prot25$SUM = NULL #remove SUM column
CD_NVC_EFS_prot25$protein = rownames(CD_NVC_EFS_prot25) #add protein column if not showing up
CD_NVC_EFS_pro25tLong = gather(CD_NVC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_NVC_EFS_pro25tLong = merge(gene_names, CD_NVC_EFS_pro25tLong) #merge gene_names
ggplot(CD_NVC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CD_NVI_EFS_score_sum = colSums(CD_NVI_EFS) # add sum of scores
CD_NVI_EFS_protsums = rbind(CD_NVI_EFS, CD_NVI_EFS_score_sum) # attach summed score for filtering in future step
rownames(CD_NVI_EFS_protsums)[rownames(CD_NVI_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CD_NVI_EFS_protsumsT = t(CD_NVI_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CD_NVI_EFS_protsumsT = as.data.frame(CD_NVI_EFS_protsumsT) # made data frame
CD_NVI_EFS_prot25 = subset(CD_NVI_EFS_protsumsT, CD_NVI_EFS_protsumsT$CD_NVI_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CD_NVI_EFS_prot25$SUM = NULL #remove SUM column
CD_NVI_EFS_prot25$protein = rownames(CD_NVI_EFS_prot25) #add protein column if not showing up
CD_NVI_EFS_pro25tLong = gather(CD_NVI_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_NVI_EFS_pro25tLong = merge(gene_names, CD_NVI_EFS_pro25tLong) #merge gene_names
ggplot(CD_NVI_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CD_NVIC_EFS_score_sum = colSums(CD_NVIC_EFS) # add sum of scores
CD_NVIC_EFS_protsums = rbind(CD_NVIC_EFS, CD_NVIC_EFS_score_sum) # attach summed score for filtering in future step
rownames(CD_NVIC_EFS_protsums)[rownames(CD_NVIC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CD_NVIC_EFS_protsumsT = t(CD_NVIC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CD_NVIC_EFS_protsumsT = as.data.frame(CD_NVIC_EFS_protsumsT) # made data frame
CD_NVIC_EFS_prot25 = subset(CD_NVIC_EFS_protsumsT, CD_NVIC_EFS_protsumsT$CD_NVIC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CD_NVIC_EFS_prot25$SUM = NULL #remove SUM column
CD_NVIC_EFS_prot25$protein = rownames(CD_NVIC_EFS_prot25) #add protein column if not showing up
CD_NVIC_EFS_pro25tLong = gather(CD_NVIC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_NVIC_EFS_pro25tLong = merge(gene_names, CD_NVIC_EFS_pro25tLong) #merge gene_names
ggplot(CD_NVIC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```


```{r}
SES_MIvMS_EFS_score_sum = colSums(SES_MIvMS_EFS) # add sum of scores
SES_MIvMS_EFS_protsums = rbind(SES_MIvMS_EFS, SES_MIvMS_EFS_score_sum) # attach summed score for filtering in future step
rownames(SES_MIvMS_EFS_protsums)[rownames(SES_MIvMS_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
SES_MIvMS_EFS_protsumsT = t(SES_MIvMS_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
SES_MIvMS_EFS_protsumsT = as.data.frame(SES_MIvMS_EFS_protsumsT) # made data frame
SES_MIvMS_EFS_prot25 = subset(SES_MIvMS_EFS_protsumsT, SES_MIvMS_EFS_protsumsT$SES_MIvMS_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
SES_MIvMS_EFS_prot25$SUM = NULL #remove SUM column
SES_MIvMS_EFS_prot25$protein = rownames(SES_MIvMS_EFS_prot25) #add protein column if not showing up
SES_MIvMS_EFS_pro25tLong = gather(SES_MIvMS_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_NVIC_EFS_pro25tLong = merge(gene_names, CD_NVIC_EFS_pro25tLong) #merge gene_names
ggplot(SES_MIvMS_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CDColvUC_EFS_score_sum = colSums(CDColvUC_EFS) # add sum of scores
CDColvUC_EFS_protsums = rbind(CDColvUC_EFS, CDColvUC_EFS_score_sum) # attach summed score for filtering in future step
rownames(CDColvUC_EFS_protsums)[rownames(CDColvUC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CDColvUC_EFS_protsumsT = t(CDColvUC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CDColvUC_EFS_protsumsT = as.data.frame(CDColvUC_EFS_protsumsT) # made data frame
CDColvUC_EFS_prot25 = subset(CDColvUC_EFS_protsumsT, CDColvUC_EFS_protsumsT$CDColvUC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CDColvUC_EFS_prot25$SUM = NULL #remove SUM column
CDColvUC_EFS_prot25$protein = rownames(CDColvUC_EFS_prot25) #add protein column if not showing up
CDColvUC_EFS_pro25tLong = gather(CDColvUC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_NVIC_EFS_pro25tLong = merge(gene_names, CD_NVIC_EFS_pro25tLong) #merge gene_names
ggplot(CDColvUC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```

```{r}
CDilvUC_EFS_score_sum = colSums(CDilvUC_EFS) # add sum of scores
CDilvUC_EFS_protsums = rbind(CDilvUC_EFS, CDilvUC_EFS_score_sum) # attach summed score for filtering in future step
rownames(CDilvUC_EFS_protsums)[rownames(CDilvUC_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CDilvUC_EFS_protsumsT = t(CDilvUC_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CDilvUC_EFS_protsumsT = as.data.frame(CDilvUC_EFS_protsumsT) # made data frame
CDilvUC_EFS_prot25 = subset(CDilvUC_EFS_protsumsT, CDilvUC_EFS_protsumsT$CDilvUC_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CDilvUC_EFS_prot25$SUM = NULL #remove SUM column
CDilvUC_EFS_prot25$protein = rownames(CDilvUC_EFS_prot25) #add protein column if not showing up
CDilvUC_EFS_pro25tLong = gather(CDilvUC_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_NVIC_EFS_pro25tLong = merge(gene_names, CD_NVIC_EFS_pro25tLong) #merge gene_names
ggplot(CDilvUC_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```



```{r}
CDOnlyUlcer_EFS_score_sum = colSums(CDOnlyUlcer_EFS) # add sum of scores
CDOnlyUlcer_EFS_protsums = rbind(CDOnlyUlcer_EFS, CDOnlyUlcer_EFS_score_sum) # attach summed score for filtering in future step
rownames(CDOnlyUlcer_EFS_protsums)[rownames(CDOnlyUlcer_EFS_protsums) == "9"] = "SUM" #change 9 column to "SUM"
CDOnlyUlcer_EFS_protsumsT = t(CDOnlyUlcer_EFS_protsums) # transform DF to correct orientation (metrics as cols, proteins as rows)
CDOnlyUlcer_EFS_protsumsT = as.data.frame(CDOnlyUlcer_EFS_protsumsT) # made data frame
CDOnlyUlcer_EFS_prot25 = subset(CDOnlyUlcer_EFS_protsumsT, CDOnlyUlcer_EFS_protsumsT$CDOnlyUlcer_EFS_score_sum > EFS_level) #subset to just proteins whos summed scores are above EFS_level
CDOnlyUlcer_EFS_prot25$SUM = NULL #remove SUM column
CDOnlyUlcer_EFS_prot25$protein = rownames(CDOnlyUlcer_EFS_prot25) #add protein column if not showing up
CDOnlyUlcer_EFS_pro25tLong = gather(CDOnlyUlcer_EFS_prot25, key = metric, value = measurement, 1:8, factor_key = T) #longform data
## CD_NVIC_EFS_pro25tLong = merge(gene_names, CD_NVIC_EFS_pro25tLong) #merge gene_names
ggplot(CDOnlyUlcer_EFS_pro25tLong, aes(x = reorder(protein, measurement), y = measurement, fill = metric)) + geom_bar(stat = "identity") + theme_bw() + coord_flip() #plot with bargraph
```


rename column, make unique protein only DF
```{r}
IBD_HC_EFS_unique = as.data.frame(unique(IBDvHC_EFS_pro25tLong$protein))
colnames(IBD_HC_EFS_unique)[colnames(IBD_HC_EFS_unique) == "unique(IBDvHC_EFS_pro25tLong$protein)"] = "Proteins"
IBD_HC_EFS_unique = c("OTU_ID", "Study_group", IBD_HC_EFS_unique$Proteins)

## CD v UC
CDvUC_EFS_unique = as.data.frame(unique(CDvUC_EFS_pro25tLong$protein))
colnames(CDvUC_EFS_unique)[colnames(CDvUC_EFS_unique) == "unique(CDvUC_EFS_pro25tLong$protein)"] = "Proteins"
CDvUC_EFS_unique = c("OTU_ID","Diagnosis", CDvUC_EFS_unique$Proteins)

## CD location
CD_CVIC_EFS_unique = as.data.frame(unique(CD_CVIC_EFS_pro25tLong$protein))
colnames(CD_CVIC_EFS_unique)[colnames(CD_CVIC_EFS_unique) == "unique(CD_CVIC_EFS_pro25tLong$protein)"] = "Proteins"
CD_CVIC_EFS_unique = c("OTU_ID","Active_Location", CD_CVIC_EFS_unique$Proteins)

CD_IVC_EFS_unique = as.data.frame(unique(CD_IVC_EFS_pro25tLong$protein))
colnames(CD_IVC_EFS_unique)[colnames(CD_IVC_EFS_unique) == "unique(CD_IVC_EFS_pro25tLong$protein)"] = "Proteins"
CD_IVC_EFS_unique = c("OTU_ID","Active_Location", CD_IVC_EFS_unique$Proteins)

CD_IVIC_EFS_unique = as.data.frame(unique(CD_IVIC_EFS_pro25tLong$protein))
colnames(CD_IVIC_EFS_unique)[colnames(CD_IVIC_EFS_unique) == "unique(CD_IVIC_EFS_pro25tLong$protein)"] = "Proteins"
CD_IVIC_EFS_unique = c("OTU_ID","Active_Location", CD_IVIC_EFS_unique$Proteins)

CD_NVC_EFS_unique = as.data.frame(unique(CD_NVC_EFS_pro25tLong$protein))
colnames(CD_NVC_EFS_unique)[colnames(CD_NVC_EFS_unique) == "unique(CD_NVC_EFS_pro25tLong$protein)"] = "Proteins"
CD_NVC_EFS_unique = c("OTU_ID","Active_Location", CD_NVC_EFS_unique$Proteins)

CD_NVI_EFS_unique = as.data.frame(unique(CD_NVI_EFS_pro25tLong$protein))
colnames(CD_NVI_EFS_unique)[colnames(CD_NVI_EFS_unique) == "unique(CD_NVI_EFS_pro25tLong$protein)"] = "Proteins"
CD_NVI_EFS_unique = c("OTU_ID","Active_Location", CD_NVI_EFS_unique$Proteins)

CD_NVIC_EFS_unique = as.data.frame(unique(CD_NVIC_EFS_pro25tLong$protein))
colnames(CD_NVIC_EFS_unique)[colnames(CD_NVIC_EFS_unique) == "unique(CD_NVIC_EFS_pro25tLong$protein)"] = "Proteins"
CD_NVIC_EFS_unique = c("OTU_ID","Active_Location", CD_NVIC_EFS_unique$Proteins)

##severity
SES_MIvMS_EFS_unique = as.data.frame(unique(SES_MIvMS_EFS_pro25tLong$protein))
colnames(SES_MIvMS_EFS_unique)[colnames(SES_MIvMS_EFS_unique) == "unique(SES_MIvMS_EFS_pro25tLong$protein)"] = "Proteins"
SES_MIvMS_EFS_unique = c("OTU_ID","SES_group", SES_MIvMS_EFS_unique$Proteins)

## ulcer
CDOnly_ulcer_EFS_unique = as.data.frame(unique(CDOnlyUlcer_EFS_pro25tLong$protein))
colnames(CDOnly_ulcer_EFS_unique)[colnames(CDOnly_ulcer_EFS_unique) == "unique(CDOnlyUlcer_EFS_pro25tLong$protein)"] = "Proteins"
CDOnly_ulcer_EFS_unique = c("OTU_ID","Ulcer_group", CDOnly_ulcer_EFS_unique$Proteins)


## UC v CD colonic
CDColvUC_EFS_unique = as.data.frame(unique(CDColvUC_EFS_pro25tLong$protein))
colnames(CDColvUC_EFS_unique)[colnames(CDColvUC_EFS_unique) == "unique(CDColvUC_EFS_pro25tLong$protein)"] = "Proteins"
CDColvUC_EFS_unique = c("OTU_ID","Diagnosis", CDColvUC_EFS_unique$Proteins)


## UC v CD ileal
CDilvUC_EFS_unique = as.data.frame(unique(CDilvUC_EFS_pro25tLong$protein))
colnames(CDilvUC_EFS_unique)[colnames(CDilvUC_EFS_unique) == "unique(CDilvUC_EFS_pro25tLong$protein)"] = "Proteins"
CDilvUC_EFS_unique = c("OTU_ID","Diagnosis", CDilvUC_EFS_unique$Proteins)
```


```{r}
## IBDvHC
## train
IBDvHC_train_EFS_subset = subset(train_data, select = IBD_HC_EFS_unique)
rownames(IBDvHC_train_EFS_subset) = samples
## test
IBDvHC_test_EFS_subset = subset(testing_data, select = IBD_HC_EFS_unique)
rownames(IBDvHC_test_EFS_subset) = IBD_testing_samples

## CD v UC
## train
CDvUC_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_CDvUC_samples)
CDvUC_train_EFS_subset = subset(CDvUC_train_EFS_subset, select = CDvUC_EFS_unique)
rownames(CDvUC_train_EFS_subset) = TRAIN_CDvUC_samples
## test
CDvUC_test_EFS_subset = subset(testing_data, OTU_ID %in% CDvUC_testing_samples)
CDvUC_test_EFS_subset = subset(CDvUC_test_EFS_subset, select = CDvUC_EFS_unique)
rownames(CDvUC_test_EFS_subset) = CDvUC_testing_samples


## Severity
## train
SES_MIvMS_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_SES_MIvMS_samples)
SES_MIvMS_train_EFS_subset = subset(SES_MIvMS_train_EFS_subset, select = SES_MIvMS_EFS_unique)
rownames(SES_MIvMS_train_EFS_subset) = TRAIN_SES_MIvMS_samples
## test
SES_MIvMS_test_EFS_subset = subset(testing_data, OTU_ID %in% SES_MIvMS_testing_samples)
SES_MIvMS_test_EFS_subset = subset(SES_MIvMS_test_EFS_subset, select = SES_MIvMS_EFS_unique)
rownames(SES_MIvMS_test_EFS_subset) = SES_MIvMS_testing_samples


## Inflammatory location
## train
CD_CVIC_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_CVIC_samples)
CD_CVIC_train_EFS_subset = subset(CD_CVIC_train_EFS_subset, select = CD_CVIC_EFS_unique)
rownames(CD_CVIC_train_EFS_subset) = TRAIN_CVIC_samples
## test
CD_CVIC_test_EFS_subset = subset(testing_data, OTU_ID %in% CD_CVIC_testing_samples)
CD_CVIC_test_EFS_subset = subset(CD_CVIC_test_EFS_subset, select = CD_CVIC_EFS_unique)
rownames(CD_CVIC_test_EFS_subset) = CD_CVIC_testing_samples

## train
CD_NVIC_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_NVIC_samples)
CD_NVIC_train_EFS_subset = subset(CD_NVIC_train_EFS_subset, select = CD_NVIC_EFS_unique)
rownames(CD_NVIC_train_EFS_subset) = TRAIN_NVIC_samples
## test
CD_NVIC_test_EFS_subset = subset(testing_data, OTU_ID %in% CD_NVIC_testing_samples)
CD_NVIC_test_EFS_subset = subset(CD_NVIC_test_EFS_subset, select = CD_NVIC_EFS_unique)
rownames(CD_NVIC_test_EFS_subset) = CD_NVIC_testing_samples

## train
CD_NVI_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_NVI_samples)
CD_NVI_train_EFS_subset = subset(CD_NVI_train_EFS_subset, select = CD_NVI_EFS_unique)
rownames(CD_NVI_train_EFS_subset) = TRAIN_NVI_samples
## test
CD_NVI_test_EFS_subset = subset(testing_data, OTU_ID %in% CD_NVI_testing_samples)
CD_NVI_test_EFS_subset = subset(CD_NVI_test_EFS_subset, select = CD_NVI_EFS_unique)
rownames(CD_NVI_test_EFS_subset) = CD_NVI_testing_samples

## train
CD_NVC_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_NVC_samples)
CD_NVC_train_EFS_subset = subset(CD_NVC_train_EFS_subset, select = CD_NVC_EFS_unique)
rownames(CD_NVC_train_EFS_subset) = TRAIN_NVC_samples
## test
CD_NVC_test_EFS_subset = subset(testing_data, OTU_ID %in% CD_NVC_testing_samples)
CD_NVC_test_EFS_subset = subset(CD_NVC_test_EFS_subset, select = CD_NVC_EFS_unique)
rownames(CD_NVC_test_EFS_subset) = CD_NVC_testing_samples

## train
CD_IVC_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_IVC_samples)
CD_IVC_train_EFS_subset = subset(CD_IVC_train_EFS_subset, select = CD_IVC_EFS_unique)
rownames(CD_IVC_train_EFS_subset) = TRAIN_IVC_samples
## test
CD_IVC_test_EFS_subset = subset(testing_data, OTU_ID %in% CD_IVC_testing_samples)
CD_IVC_test_EFS_subset = subset(CD_IVC_test_EFS_subset, select = CD_IVC_EFS_unique)
rownames(CD_IVC_test_EFS_subset) = CD_IVC_testing_samples

## train
CD_IVIC_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_IVIC_samples)
CD_IVIC_train_EFS_subset = subset(CD_IVIC_train_EFS_subset, select = CD_IVIC_EFS_unique)
rownames(CD_IVIC_train_EFS_subset) = TRAIN_IVIC_samples
## test
CD_IVIC_test_EFS_subset = subset(testing_data, OTU_ID %in% CD_IVIC_testing_samples)
CD_IVIC_test_EFS_subset = subset(CD_IVIC_test_EFS_subset, select = CD_IVIC_EFS_unique)
rownames(CD_IVIC_test_EFS_subset) = CD_IVIC_testing_samples

## Ulcer
## train
CDOnly_ulcer_train_EFS_subset = subset(train_data, OTU_ID %in% TRAIN_ULCER_samples)
CDOnly_ulcer_train_EFS_subset = subset(CDOnly_ulcer_train_EFS_subset, select = CDOnly_ulcer_EFS_unique)
rownames(CDOnly_ulcer_train_EFS_subset) = TRAIN_ULCER_samples
## test
CDOnly_ulcer_test_EFS_subset = subset(testing_data, OTU_ID %in% CDUlcer_testing_samples)
CDOnly_ulcer_test_EFS_subset = subset(CDOnly_ulcer_test_EFS_subset, select = CDOnly_ulcer_EFS_unique)
rownames(CDOnly_ulcer_test_EFS_subset) = CDUlcer_testing_samples

## train
CDCol_v_UC_train_EFS_subset = subset(train_data, OTU_ID %in% CDCol_v_UC_samples)
CDCol_v_UC_train_EFS_subset = subset(CDCol_v_UC_train_EFS_subset, select = CDColvUC_EFS_unique)
rownames(CDCol_v_UC_train_EFS_subset) = CDCol_v_UC_samples
## test
CDCol_v_UC_test_EFS_subset = subset(testing_data, OTU_ID %in% CDColvUC_testing_samples)
CDCol_v_UC_test_EFS_subset = subset(CDCol_v_UC_test_EFS_subset, select = CDColvUC_EFS_unique)
rownames(CDCol_v_UC_test_EFS_subset) = CDColvUC_testing_samples

## train
CDil_v_UC_train_EFS_subset = subset(train_data, OTU_ID %in% CDil_v_UC_samples)
CDil_v_UC_train_EFS_subset = subset(CDil_v_UC_train_EFS_subset, select = CDilvUC_EFS_unique)
rownames(CDil_v_UC_train_EFS_subset) = CDil_v_UC_samples
## test
CDil_v_UC_test_EFS_subset = subset(testing_data, OTU_ID %in% CDilvUC_testing_samples)
CDil_v_UC_test_EFS_subset = subset(CDil_v_UC_test_EFS_subset, select = CDilvUC_EFS_unique)
rownames(CDil_v_UC_test_EFS_subset) = CDilvUC_testing_samples
```

recode classifications for algos
```{r}
IBDvHC_train_EFS_subset$Study_group = as.numeric(revalue(IBDvHC_train_EFS_subset$Study_group, c("HC" = 0, "IBD" = 1)))
IBDvHC_test_EFS_subset$Study_group = as.numeric(revalue(IBDvHC_test_EFS_subset$Study_group, c("HC" = 0, "IBD" = 1)))

CDvUC_train_EFS_subset$Diagnosis = as.numeric(revalue(CDvUC_train_EFS_subset$Diagnosis, c("UC" = 0, "CD" = 1)))
CDvUC_test_EFS_subset$Diagnosis = as.numeric(revalue(CDvUC_test_EFS_subset$Diagnosis, c("UC" = 0, "CD" = 1)))

## severity
SES_MIvMS_train_EFS_subset$SES_group = as.numeric(revalue(SES_MIvMS_train_EFS_subset$SES_group, c("inactive_mild" = 0, "moderate_severe" = 1)))
SES_MIvMS_test_EFS_subset$SES_group = as.numeric(revalue(SES_MIvMS_test_EFS_subset$SES_group, c("inactive_mild" = 0, "moderate_severe" = 1)))

## Inflammatory location
CD_CVIC_train_EFS_subset$Active_Location = as.numeric(revalue(CD_CVIC_train_EFS_subset$Active_Location, c("colonic" = 0, "ileocolonic" = 1)))
CD_CVIC_test_EFS_subset$Active_Location = as.numeric(revalue(CD_CVIC_test_EFS_subset$Active_Location, c("colonic" = 0, "ileocolonic" = 1)))

CD_NVIC_train_EFS_subset$Active_Location = as.numeric(revalue(CD_NVIC_train_EFS_subset$Active_Location, c("none" = 0, "ileocolonic" = 1)))
CD_NVIC_test_EFS_subset$Active_Location = as.numeric(revalue(CD_NVIC_test_EFS_subset$Active_Location, c("none" = 0, "ileocolonic" = 1)))

CD_NVI_train_EFS_subset$Active_Location = as.numeric(revalue(CD_NVI_train_EFS_subset$Active_Location, c("none" = 0, "ileal" = 1)))
CD_NVI_test_EFS_subset$Active_Location = as.numeric(revalue(CD_NVI_test_EFS_subset$Active_Location, c("none" = 0, "ileal" = 1)))

CD_NVC_train_EFS_subset$Active_Location = as.numeric(revalue(CD_NVC_train_EFS_subset$Active_Location, c("none" = 0, "colonic" = 1)))
CD_NVC_test_EFS_subset$Active_Location = as.numeric(revalue(CD_NVC_test_EFS_subset$Active_Location, c("none" = 0, "colonic" = 1)))

CD_IVC_train_EFS_subset$Active_Location = as.numeric(revalue(CD_IVC_train_EFS_subset$Active_Location, c("ileal" = 0, "colonic" = 1)))
CD_IVC_test_EFS_subset$Active_Location = as.numeric(revalue(CD_IVC_test_EFS_subset$Active_Location, c("ileal" = 0, "colonic" = 1)))

CD_IVIC_train_EFS_subset$Active_Location = as.numeric(revalue(CD_IVIC_train_EFS_subset$Active_Location, c("ileal" = 0, "ileocolonic" = 1)))
CD_IVIC_test_EFS_subset$Active_Location = as.numeric(revalue(CD_IVIC_test_EFS_subset$Active_Location, c("ileal" = 0, "ileocolonic" = 1)))

## Ulcer
CDOnly_ulcer_train_EFS_subset$Ulcer_group = as.numeric(revalue(CDOnly_ulcer_train_EFS_subset$Ulcer_group, c("rem_mild" = 0, "mod_sev" = 1)))
CDOnly_ulcer_test_EFS_subset$Ulcer_group = as.numeric(revalue(CDOnly_ulcer_test_EFS_subset$Ulcer_group, c("rem_mild" = 0, "mod_sev" = 1)))

## CD Colonic vs UC
CDCol_v_UC_train_EFS_subset$Diagnosis = as.numeric(revalue(CDCol_v_UC_train_EFS_subset$Diagnosis, c("UC" = 0, "CD" = 1)))
CDCol_v_UC_test_EFS_subset$Diagnosis= as.numeric(revalue(CDCol_v_UC_test_EFS_subset$Diagnosis, c("UC" = 0, "CD" = 1)))

## CD Ileal vs UC
CDil_v_UC_train_EFS_subset$Diagnosis = as.numeric(revalue(CDil_v_UC_train_EFS_subset$Diagnosis, c("UC" = 0, "CD" = 1)))
CDil_v_UC_test_EFS_subset$Diagnosis= as.numeric(revalue(CDil_v_UC_test_EFS_subset$Diagnosis, c("UC" = 0, "CD" = 1)))
```

create splits dir and write text files
```{r}
dir.create("EFS_selected_data_sets")
dir.create("EFS_selected_data_sets/CDvUC")
dir.create("EFS_selected_data_sets/Severity")
dir.create("EFS_selected_data_sets/Location")
dir.create("EFS_selected_data_sets/Ulcer")
dir.create("EFS_selected_data_sets/IBDvHC")

## IBD  v healthy info
write.csv(IBDvHC_train_EFS_subset, "EFS_selected_data_sets/IBDvHC/IBDvHC_train_EFS_selected.csv", row.names = F)
write.csv(IBDvHC_test_EFS_subset, "EFS_selected_data_sets/IBDvHC/IBDvHC_test_EFS_selected.csv", row.names = F)

## CD location info
write.csv(CDvUC_train_EFS_subset, "EFS_selected_data_sets/CDvUC/CDvUC_train_EFS_selected.csv", row.names = F)
write.csv(CDvUC_test_EFS_subset, "EFS_selected_data_sets/CDvUC/CDvUC_test_EFS_selected.csv", row.names = F)

write.csv(CD_CVIC_train_EFS_subset, "EFS_selected_data_sets/Location/CD_CVIC_train_EFS_selected.csv", row.names = F)
write.csv(CD_CVIC_test_EFS_subset, "EFS_selected_data_sets/Location/CD_CVIC_test_EFS_selected.csv", row.names = F)

write.csv(CD_IVC_train_EFS_subset, "EFS_selected_data_sets/Location/CD_IVC_train_EFS_selected.csv", row.names = F)
write.csv(CD_IVC_test_EFS_subset, "EFS_selected_data_sets/Location/CD_IVC_test_EFS_selected.csv", row.names = F)

write.csv(CD_IVIC_train_EFS_subset, "EFS_selected_data_sets/Location/CD_IVIC_train_EFS_selected.csv", row.names = F)
write.csv(CD_IVIC_test_EFS_subset, "EFS_selected_data_sets/Location/CD_IVIC_test_EFS_selected.csv", row.names = F)

write.csv(CD_NVI_train_EFS_subset, "EFS_selected_data_sets/Location/CD_NVI_train_EFS_selected.csv", row.names = F)
write.csv(CD_NVI_test_EFS_subset, "EFS_selected_data_sets/Location/CD_NVI_test_EFS_selected.csv", row.names = F)

write.csv(CD_NVC_train_EFS_subset, "EFS_selected_data_sets/Location/CD_NVC_train_EFS_selected.csv", row.names = F)
write.csv(CD_NVC_test_EFS_subset, "EFS_selected_data_sets/Location/CD_NVC_test_EFS_selected.csv", row.names = F)

write.csv(CD_NVIC_train_EFS_subset, "EFS_selected_data_sets/Location/CD_NVIC_train_EFS_selected.csv", row.names = F)
write.csv(CD_NVIC_test_EFS_subset, "EFS_selected_data_sets/Location/CD_NVIC_test_EFS_selected.csv", row.names = F)

## ulcer class info
write.csv(CDOnly_ulcer_train_EFS_subset, "EFS_selected_data_sets/Ulcer/CDOnly_ulcer_train_EFS_selected.csv", row.names = F)
write.csv(CDOnly_ulcer_test_EFS_subset, "EFS_selected_data_sets/Ulcer/CDOnly_ulcer_test_EFS_selected.csv", row.names = F)

## UC vs CD colonic/ileal
write.csv(CDCol_v_UC_train_EFS_subset, "EFS_selected_data_sets/CDvUC/CDCol_v_UC_train_EFS_selected.csv", row.names = F)
write.csv(CDCol_v_UC_test_EFS_subset, "EFS_selected_data_sets/CDvUC/CDCol_v_UC_test_EFS_selected.csv", row.names = F)

write.csv(CDil_v_UC_train_EFS_subset, "EFS_selected_data_sets/CDvUC/CDil_v_UC_train_EFS_selected.csv", row.names = F)
write.csv(CDil_v_UC_test_EFS_subset, "EFS_selected_data_sets/CDvUC/CDil_v_UC_test_EFS_selected.csv", row.names = F)

## SES Group
write.csv(SES_MIvMS_train_EFS_subset, "EFS_selected_data_sets/Severity/SES_MIvMS_train_EFS_selected.csv", row.names = F)
write.csv(SES_MIvMS_test_EFS_subset, "EFS_selected_data_sets/Severity/SES_MIvMS_test_EFS_selected.csv", row.names = F)
```


```{r}
##!!!
```

